Gravitaitonal Wave Event Progenitor Synthesis

### 2022-05-26 src/tex/ms.tex
Add rodrigo to the author list
Add rodrigo's email
Minor updates.

\begin{abstract}
One promising way to extract information about stellar astrophysics from
gravitational wave catalogs is to compare the catalog to the outputs of stellar
population synthesis modeling with varying physical assumptions.  The parameter
space of physical assumptions in population synthesis is high-dimensional and
the choice of parameters that best represents the evolution of a binary system
may depend on an as-yet-to-be-determined way on the system's properties. Indeed,
measuring the variation of population synthesis parameter settings with binary
properties is one of the principal ways to extract information about binary
evolution from catalogs. Here we propose an inference pipeline to simultaneously
infer zero-age main sequence properties and population synthesis parameter
settings controlling modeled binary evolution from individual gravitational wave
observations of merging compact binaries.  Our pipeline can efficiently explore
the high-dimensional space of population synthesis settings and progenitor
system properties for each system in a catalog of gravitational wave
observations.  We apply our pipeline to observations in the third LIGO Virgo
Kagra Gravitational Wave Transient Catalog.
We showcase the effectiveness of this pipeline with a detailed study
of the progenitor properties and population synthesis settings that produce
mergers like the observed GW150914.
\end{abstract}

>>>>

\begin{abstract}
One promising way to extract information about stellar astrophysics from
gravitational wave catalogs is to compare the catalog to the outputs of stellar
population synthesis modeling with varying physical assumptions.  The parameter
space of physical assumptions in population synthesis is high-dimensional and
the choice of parameters that best represents the evolution of a binary system
may depend on an as-yet-to-be-determined way on the system's properties. Indeed,
measuring the variation of population synthesis parameter settings with binary
properties is one of the principal ways to extract information about binary
evolution from catalogs. Here we propose a pipeline to simultaneously infer
zero-age main sequence properties and population synthesis parameter settings
controlling modeled binary evolution from individual gravitational wave
observations of merging compact binaries.  Our pipeline can efficiently explore
the high-dimensional space of population synthesis settings and progenitor
system properties for each system in a catalog of gravitational wave
observations.  We apply our pipeline to observations in the third LIGO Virgo
Kagra Gravitational Wave Transient Catalog. We showcase the effectiveness of
this pipeline with a detailed study of the progenitor properties and population
synthesis settings that produce mergers like the observed GW150914.
\end{abstract}
